Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
Remove trailing whitespace
fix mixups in lattice model subsection

\begin{defn}{(\emph{Points})}
  A $N$-dimenaional \emph{point} is a finite Cartesian product
  (vector) of $N$ values drawn from $\zinf$.

  The set of $N$-dimensional points is written $\zinf^N$ and the set
  of sets of $N$-dimensionl points is written $\mathcal{P}(\zinf^N)$.

A set of $N$-dimensional points can be \emph{projected} to the set of
1-dimensional points in the $i^{\text{th}}$ dimension by
$\pi_i : \mathcal{P}(\zinf{}^{\mkern0mu{N}}) \to
\mathcal{P}(\zinf{})$
where $i \in \mathsf{Fin}(N)$. We refer to this projected set as the
\emph{$i^{th}$ components}.
\end{defn}

\begin{prop}
The set $\mathcal{P}{(\zinf{}^{{N}})}$ trivially forms a
  distributive lattice under the superset relation.
\end{prop}

\begin{remark}
Note that $\mathcal{P}(\zinf^N)$ is isomorphic to a sets of point
vectors $\mathcal{P}(\zinf)^N$. Therefore, projection $\pi$ on 
offset spaces is defined by lifting normal Cartesian product
projection to sets.
\end{remark}

%\begin{defn}{(\emph{Offsets vector}, $\mathcal{P}(\zinf^N)$)}
%  An $N$ dimensional \emph{offset space vector} is a Cartesian product of offset
%  spaces denoted with $\textit{offs}_1 \times \cdots \times
%  \textit{offs}_N$.
%  The function $\pi_i : \mathcal{P}(\zinf{})^{\mkern-19mu{N}} \to
%  \mathcal{P}(\zinf{})$ retrieves the $i^{th}$ offset space.%
%
%  The set of $N$ dimensional offsets vectors is
%  $\mathcal{P}{(\zinf{}^{\mkern-19mu{N}})}$ and they trivially form a
%  distributive lattice under the superset relation.
%\end{defn}

\begin{defn}{(\emph{Subscript})}
  A set of $N$-dimensional points $S$ is called a \emph{subscript} if it
  satisfies:
%
\begin{equation*}
\forall i \in \textsf{Fin}(N) . \quad 
\pi_i (S) = \{p\} \wedge p \in \mathbb{Z} 
\;\;
\vee
\;\;
\pi_i (S) = \interv{-\infty}{\infty}{\mathsf{true}}
\end{equation*}
%
That is, the $i^{th}$ component of the set is either a singleton 
in $\mathbb{Z}$ or the infinite interval.

\todo{We can move this explanation.}
Subscript spaces model array subscript expressions in our source
langauge where each subscripted expression is either a 
constant translation of an induction variable within a loop or some
other expression which is constant with respect to the loop e.g. \texttt{a(i + 1, 0)}.
\end{defn}

@@

\begin{defn}{(\emph{Point interval})}
An point interval is a finite Cartesian product of intervals on \zinf, 
denoted by the set $\textit{Interval}^N$ for a product of $N$ intervals.
\end{defn}

@@

\begin{prop}{}
  $(\region{N},\subseteq)$ is a distributive lattice.
\end{prop}
%
\begin{proof}
  Any sublattice of a distributive lattice is a distributive lattice. Power sets
  partially ordered with subset or equal to relation are distributive lattices.
  \region{N} is a subset of $\mathcal{P}{(\zinf{}^{\mkern0mu{N}})}$ since all
  vector intervals are subsets of this power set and union and intersection
  cannot add an element that is not already in the powerset.  Inductive
  definition also ensures that \region{N} is closed under these operations.
  Therefore, \region{N} is a distributive sublattice of
  $(\mathcal{P}{(\zinf{}^{\mkern0mu{N}})}, \subseteq)$.
\end{proof}

>>>>

\begin{defn}{(\emph{Offset subspace})}
  An $N$-dimenaional \emph{offset subspace} is a finite Cartesian product of $N$
  subsets of $\zinf{}$. The set of $N$-dimensional offset subspaces is written
  ${\mathcal{P}(\zinf{})}^N$.

  A offset spaces can be \emph{projected} in the $i^{\textit{th}}$ dimension by
  $\pi_i : {\mathcal{P}(\zinf{})}^N \to \mathcal{P}(\zinf{})$ where $i \in
  \mathsf{Fin}(N)$.
\end{defn}

\begin{defn}{(\emph{Subscript})}
  An $N$-dimensional offset subspace $S$ is called a \emph{subscript} if it
  satisfies:
%
  \begin{equation*}
    \forall i \in \textsf{Fin}(N).\
      \pi_i (S) = \{p\} \wedge p \in \mathbb{Z}
      \vee
      \pi_i (S) = \interv{-\infty}{\infty}{\mathsf{true}}
  \end{equation*}
  %
  That is, the $i^{th}$ component of the set is either a singleton
  in $\mathbb{Z}$ or the infinite interval.

  \todo{%
    We can move this explanation.

    Subscript spaces model array subscript expressions in our source langauge
    where each subscripted expression is either a constant translation of an
    induction variable within a loop or some other expression which is constant
    with respect to the loop e.g. \texttt{a(i+1, 0)}.
  }
\end{defn}

@@

\begin{defn}{(\emph{Interval subspace})}
  An interval subspace is a finite Cartesian product of intervals on \zinf{},
  denoted by the set $\textit{Interval}^N$ for a product of $N$ intervals. An
  interval subspace is an offset subspace.
\end{defn}

@@

\begin{prop}{}
  $(\region{N},\subseteq)$ is a distributive lattice.
\end{prop}
%
\begin{proof}
  Any sublattice of a distributive lattice is a distributive lattice. Power sets
  partially ordered with subset relation are distributive lattices. \region{N}
  is a subset of $\mathcal{P}{(\zinf{}^N)}$ since all interval subspaces are
  subsets of this power set and; union and intersection cannot add an element
  that is not already in the powerset. Inductive definition also ensures that
  \region{N} is closed under these operations. Therefore, \region{N} is a
  distributive sublattice of $(\mathcal{P}{(\zinf{}^N)}, \subseteq)$.
\end{proof}
